---
title: "Vaccine effectiveness report"
output:
  html_document:
    code_folding: hide
    keep_md: yes
  pdf_document: default
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library('tidyverse')
library('lubridate')
library('gt')
library('patchwork')

source(here::here("lib", "html_output_functions.R"))

output_dir <- here::here("output") 


vars_list <- jsonlite::fromJSON(txt=here::here("lib", "global-variables.json"))

data_vaccinated <- read_rds(here::here("output", "data", "data_vaccinated.rds"))

summary_stats <- append(
  vars_list,
  list(
    run_date =date(file.info(here::here("metadata","extract_vaccinated.log"))$ctime),
    total_vaccinated = sum(!is.na(data_vaccinated$covid_vax_1_date)),
    total_vaccinated_az = sum(data_vaccinated$covid_vax_1_type=="Ox-AZ", na.rm=TRUE),
    total_vaccinated_pfizer = sum(data_vaccinated$covid_vax_1_type=="P-BNT", na.rm=TRUE)
  )
)

pct <- scales::label_percent(accuracy=0.1)


bar_theme <- 
  theme_bw(base_size = 9) + 
  theme(
    panel.border = element_blank(), #axis.line.x = element_line(colour = "black"),
    panel.grid = element_blank(),
    panel.grid.major.x = element_line(colour="grey"),
    axis.ticks = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0),
    plot.title = element_text(hjust = 0),
    plot.title.position = "plot",
    plot.caption.position =  "plot",
    plot.caption = element_text(hjust = 0, face= "italic")
  )



```

## Vaccine effectiveness data in OpenSAFELY-TPP data

This document reports the frequency of covid-related outcomes in TPP-registered patients who have received a vaccine for SARS-CoV-2. 
This is a technical document to help inform the design of vaccine effectiveness Studies in OpenSAFELY. Only patients who have received the vaccine are included, and **no inferences should be made about the comparative effectiveness between vaccinated and unvaccinated patient, between vaccine brands, or across different patient groups**. 

Measured outcomes include:

* Positive Covid case identification in primary care, using the following clinical codes:
  * [probable covid](https://codelists.opensafely.org/codelist/opensafely/covid-identification-in-primary-care-probable-covid-clinical-code/2020-07-16)
  * [positive covid test](https://codelists.opensafely.org/codelist/opensafely/covid-identification-in-primary-care-probable-covid-positive-test/2020-07-16/)
  * [covid sequelae](https://codelists.opensafely.org/codelist/opensafely/covid-identification-in-primary-care-probable-covid-sequelae/2020-07-16/)
* Positive SARS-CoV-2 test, as reported via the Second Generation Surveillance System (SGSS)
* Covid-related hospital admission, where [Covid](https://codelists.opensafely.org/codelist/opensafely/covid-identification/2020-06-03/) is listed as a reason for admission.
* Covid-related death, where [Covid](https://codelists.opensafely.org/codelist/opensafely/covid-identification/2020-06-03/) is mentioned anywhere on the death certificate.
* All-cause death.

### Data notes

The code and data for this report can be found at the [covid-vaccine-effectiveness-research GitHub repository](https://github.com/opensafely/covid-vaccine-effectiveness-research). 

The dataset used for this report was created using the study definition `/analysis/study_definition.py`, using codelists referenced in `/codelists/codelists.txt`. It was extracted from the OpenSAFELY-TPP data extracted on `r summary_stats$run_date`, with event dates censored on (occurring no later than) `r summary_stats$end_date`.

To minimise data disclosivity in frequency tables, counts are rounded to the nearest 7 and percentages are derived from these rounded counts.


```{r tte_rate_function, echo=FALSE}

print_event_rates <- function(variable,  variable_name){

  table <- read_csv(
    file.path(output_dir, "tte", "tables", paste0("event_rates_at_14days_", variable, ".csv")),
    col_types = "fiidididididid",
    na="-"
  )
  names(table)[1] <- variable_name
  
  renamer <-
  c(
    `^posPC_` = "primary care case_", 
    `^postest_` = "positive test_",
    `^admitted_` = "covid-related admission_",
    `^coviddeath_` = "covid-related death_",
    `^noncoviddeath_` = "non-covid-related death_",
    `^death_` = "all-cause death_"
  )
  
  table <- rename_with(table, ~str_replace_all(string = .x, renamer))
  
  gt_table <- table %>%
  gt() %>%
  tab_spanner_delim(delim="_", gather=TRUE) %>%
    # gather doesn't work!
    fmt_percent(
      columns = ends_with(c("%")),
      decimals = 1
    ) %>%
    fmt_missing(
      everything(),
      missing_text="-"
    ) %>%
   # cols_align(
   #   align = "left",
   #   columns = all_of(variable_name)
   # ) %>%
    tab_header(
      title = md("Post-vaccination event rates at 14 days amongst those with sufficient follow-up")
    ) %>%
    tab_source_note(
     "Numbers are rounded to the nearest 7"
    )

  return(gt_table)
}


```


```{r vaccinetype_function, echo=FALSE}

print_vaccinetype <- function(variable,  variable_name){

  table <- read_csv(
    file.path(output_dir, "vaccine_type", "tables", paste0("vaccine_type_", variable, ".csv")),
    col_types = "ffiddl",
    na="-"
  )
  
  tab <- gt_catcat(summary_catcat=table, 
            var1_name = variable_name, 
            var2_name = "vaccine type", 
            title="Vaccine type", 
            source_note = "- indicates redacted values",
            pct_decimal=1
            )
  
  return(tab)
}
```

```{r tte_barplot_function, echo=FALSE}

print_variable_freq <- function(variable, variable_name){
  
  table <- read_csv(
    file.path(output_dir, "variable_summary", "tables", paste0("categorical_", variable, ".csv")),
    col_types = cols(
      n=col_integer(),
      pct=col_double(),
      pct_nonmiss=col_double()
    )
  )
  
  ywrapwidth <- 50
  
  plotdata <- table %>%
    mutate(
      variable_explicit_na=factor(str_wrap(.level, ywrapwidth), levels=str_wrap(unique(.level), ywrapwidth))
    )
  
  plot <- ggplot(plotdata)+
    geom_bar(aes(x=n, y=variable_explicit_na), stat='identity', width=0.8)+
    geom_text(aes(x=n, y=variable_explicit_na, label=pct(pct)), hjust=-0.2)+
    #scale_x_continuous(limits=c(0, xlim_upper), breaks=seq(0,10000,1000))+
    scale_y_discrete(limits = rev(levels(plotdata$variable_explicit_na)))+
    labs(
      #title=variable_name,
      #subtitle = subtitle,
      x="Patients", 
      y=NULL
    )+
    bar_theme+
    NULL
  
  return(plot)
  
}

```


```{r tte_plotsurv_function, echo=FALSE}
  #cat("  ")
  
print_variable_patch <- function(variable){
  
  knitr::include_graphics(
    file.path(output_dir, "tte", "figures", paste0("plot_patch_",variable, ".svg"))
  )
}

```


```{r tte_hazardplot_function, echo=FALSE}
  #cat("  ")
  
print_variable_haz <- function(variable){
  
  knitr::include_graphics(
    file.path(output_dir, "tte", "figures", paste0("plot_patch_hazard_",variable, ".svg"))
  )
}

```

## Summary

As of `r summary_stats$end_date`, there were `r summary_stats$total_vaccinated` TPP-registered patients who had received at least one vaccine dose. Of these, `r summary_stats$total_vaccinated_pfizer` received the Pfizer-BioNTech (P-B) vaccine and `r summary_stats$total_vaccinated_az` received the Oxford-AstraZenica (Ox-AZ) vaccine. Brand is unknown for the remaining `r summary_stats$total_vaccinated - summary_stats$total_vaccinated_az - summary_stats$total_vaccinated_pfizer` patients.

## Summaries by patient characteristics

The tables below show, for each characteristic:

* Vaccine type, including those who have received both vaccine types
* 7-day post-vaccination event rates
* Cumulative post-vaccination event rates over time
* Estimated hazard rates over time.


### Sex

```{r sex_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("sex", "Sex")
```

&nbsp;
&nbsp;


```{r sex_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("sex", "Sex")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_sex.svg "outcomes by Sex"){width="80%"}




### Age

```{r age_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("ageband", "Age")
```

&nbsp;
&nbsp;


```{r age_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("ageband", "Age")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_ageband.svg "outcomes by Age"){width="80%"}




### Ethnicity

```{r ethnicity_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("ethnicity", "Ethnicity")
```

&nbsp;
&nbsp;


```{r ethnicity_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("ethnicity", "Ethnicity")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_ethnicity.svg "outcomes by Ethnicity"){width="80%"}


### Index of Multiple Deprivation (IMD)


```{r imd_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("imd", "IMD")
```

&nbsp;
&nbsp;


```{r imd_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("imd", "IMD")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_imd.svg "outcomes by IMD"){width="80%"}



### Region

```{r region_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("region", "Region")
```

&nbsp;
&nbsp;


```{r region_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("region", "Region")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_region.svg "outcomes by Region"){width="80%"}


### Body Mass Index

```{r bmi_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("bmi", "Body Mass Index")
```

&nbsp;
&nbsp;


```{r bmi_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("bmi", "BMI")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_bmi.svg "outcomes by BMI"){width="80%"}


### Prior infection

```{r infection_before_vax_vacc, echo=FALSE, out.width='90%', results='asis'}
print_vaccinetype("infection_before_vax", "Prior infection")
```

&nbsp;
&nbsp;


```{r infection_before_vax_tab, echo=FALSE, out.width='90%', results='asis'}
print_event_rates("infection_before_vax", "Prior infection")
```

&nbsp;
&nbsp;

![](../output/tte/figures/plot_patch_infection_before_vax.svg "outcomes by prior infection"){width="80%"}


<!-- ```{r loop, fig.width=6, echo=FALSE, message=FALSE, results='asis'} -->

<!-- for(i in c("sex", "ageband")) { -->
<!--   cat("  \n###",  i, "  \n") -->

<!--   cat("direct print here  \n") -->
<!--   print(print_vaccinetype(i, i)) -->

<!--   tab_vt <- print_vaccinetype(i, i) -->
<!--   cat("print version here  \n") -->
<!--   print(tab_vt) -->

<!--   cat("non-print version here  \n") -->
<!--   tab_vt -->

<!--   cat("  \n", "  \n") -->

<!--   print(print_event_rates(i, i)) -->

<!--   cat("  \n", "  \n") -->

<!--   print(print_variable_patch(i)) -->

<!--   cat("  \n", "  \n") -->
<!-- } -->
<!-- ``` -->








<!-- ### Chronic cardiac disease -->

<!-- ```{r ccd_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("chronic_cardiac_disease", "Chronic cardiac disease") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r ccd_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("chronic_cardiac_disease", "Chronic cardiac disease") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_chronic_cardiac_disease.svg "outcomes by chronic cardiac disease"){width="80%"} -->



<!-- ### Current COPD -->

<!-- ```{r copd_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("current_copd", "COPD") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r copd_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("current_copd", "COPD") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_current_copd.svg "outcomes by COPD"){width="80%"} -->

<!-- ### DMARDs -->

<!-- ```{r dmards_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("dmards", "DMARDs") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r dmards_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("dmards", "DMARDs") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_dmards.svg "outcomes by DMARDs"){width="80%"} -->





<!-- ### Dialysis -->

<!-- ```{r dialysis_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("dialysis", "Dialysis") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r dialysis_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("dialysis", "Dialysis") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_dialysis.svg "outcomes by Dialysis"){width="80%"} -->



<!-- ### Solid organ transplantation -->

<!-- ```{r solid_organ_transplantation_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("solid_organ_transplantation", "Solid organ transplantation") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r solid_organ_transplantation_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("solid_organ_transplantation", "Solid organ transplantation") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_solid_organ_transplantation.svg "outcomes by Solid organ transplantation"){width="80%"} -->



<!-- ### Chemo or radio-therapy -->

<!-- ```{r chemo_or_radio_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("chemo_or_radio", "Chemo or radio-therapy") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r chemo_or_radio_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("chemo_or_radio", "Chemo or radio-therapy") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_chemo_or_radio.svg "outcomes by Chemo or radio-therapy"){width="80%"} -->


<!-- ### Intellectual disability, incl. Down's -->

<!-- ```{r intel_dis_incl_downs_syndrome_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("intel_dis_incl_downs_syndrome", "Intellectual disability, incl. Down's") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r intel_dis_incl_downs_syndrome_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("intel_dis_incl_downs_syndrome", "Intellectual disability, incl. Down's") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_intel_dis_incl_downs_syndrome.svg "outcomes by Intellectual disability, incl. Down's"){width="80%"} -->



<!-- ### Lung cancer -->

<!-- ```{r lung_cancer_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("lung_cancer", "Lung cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r lung_cancer_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("lung_cancer", "Lung cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_lung_cancer.svg "outcomes by Lung cancer"){width="80%"} -->



<!-- ### Haematological cancer -->

<!-- ```{r haematological_cancer_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("haematological_cancer", "Haematological cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r haematological_cancer_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("haematological_cancer", "Haematological cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_haematological_cancer.svg "outcomes by Haematological cancer"){width="80%"} -->



<!-- ### Cancer, excluding lung and haematological cancer -->

<!-- ```{r cancer_excl_lung_and_haem_cancer_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("cancer_excl_lung_and_haem", "Cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r cancer_excl_lung_and_haem_cancer_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("cancer_excl_lung_and_haem", "Cancer") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_cancer_excl_lung_and_haem.svg "outcomes by Cancer, excluding lung and haematological cancer"){width="80%"} -->






<!-- ### Bone marrow transplant -->

<!-- ```{r bone_marrow_transplant_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("bone_marrow_transplant", "Bone marrow transplant") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r bone_marrow_transplant_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("bone_marrow_transplant", "Bone marrow transplant") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_bone_marrow_transplant.svg "outcomes by Bone marrow transplant"){width="80%"} -->




<!-- ### Cystic fibrosis -->

<!-- ```{r cystic_fibrosis_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("cystic_fibrosis", "Cystic fibrosis") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r cystic_fibrosis_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("cystic_fibrosis", "Cystic fibrosis") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_cystic_fibrosis.svg "outcomes by Cystic fibrosis"){width="80%"} -->





<!-- ### Sickle cell disease -->

<!-- ```{r sickle_cell_disease_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("sickle_cell_disease", "Sickle cell disease") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r sickle_cell_disease_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("sickle_cell_disease", "Sickle cell disease") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_sickle_cell_disease.svg "outcomes by Sickle cell disease"){width="80%"} -->




<!-- ### Permanent immunosuppression -->

<!-- ```{r permanant_immunosuppression_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("permanant_immunosuppression", "Permanent immunosuppression") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r permanant_immunosuppression_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("permanant_immunosuppression", "Permanent immunosuppression") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_permanant_immunosuppression.svg "outcomes by Permanent immunosuppression"){width="80%"} -->


<!-- ### Temporary immunosuppression -->

<!-- ```{r temporary_immunosuppression_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("temporary_immunosuppression", "Temporary immunosuppression") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r temporary_immunosuppression_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("temporary_immunosuppression", "Temporary immunosuppression") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_temporary_immunosuppression.svg "outcomes by Temporary immunosuppression"){width="80%"} -->




<!-- ### Psychosis, Schizophrenia -->

<!-- ```{r psychosis_schiz_bipolar_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("psychosis_schiz_bipolar", "Psychosis, Schizophrenia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r psychosis_schiz_bipolar_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("psychosis_schiz_bipolar", "Psychosis, Schizophrenia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_psychosis_schiz_bipolar.svg "outcomes by psychosis_schiz_bipolar"){width="80%"} -->




<!-- ### Asplenia -->

<!-- ```{r asplenia_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("asplenia", "Asplenia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r asplenia_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("asplenia", "Asplenia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_asplenia.svg "outcomes by Asplenia"){width="80%"} -->




<!-- ### Dementia -->

<!-- ```{r dementia_vacc, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_vaccinetype("dementia", "Dementia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->


<!-- ```{r dementia_tab, echo=FALSE, out.width='90%', results='asis'} -->
<!-- print_event_rates("dementia", "Dementia") -->
<!-- ``` -->

<!-- &nbsp; -->
<!-- &nbsp; -->

<!-- ![](../output/tte/figures/plot_patch_dementia.svg "outcomes by Dementia"){width="80%"} -->




